A Fully Decentralized Infrastructure for Subscription-based IoT Data Trading

### 2020-06-28 paper.tex
Reword
Add subscription concerns to related work

A. Colman et al. \cite{TrustedMarketplaceWearable} focuses on trading the sensitive data among wearables. Several security issues are well discussed and solved with DLTs in the paper, the system consists multiple components that has its different responsibilities, such as data anonymizer eliminates keen information for privacy protection, access controller handles the key management and contract manager manages Ethereum smart contracts. While the trading processes are splited into multiple servers, and the request/response communication model is applied, the scalability problem of the marketplace remains.

In the following researches, Masked Authenticated Messaging (MAM)\cite{MAM} is regarded as a secure data transmission layer and data storage built on top of DLT which provides access control, tamperproof and authentication functionalities by linking the messages to a list. Jinzhi Lu et al.\cite{luDecentralizedDM} builds the data exchange system with MAM and IPFS\cite{IPFS}, a content-based addressing distributed storage system. Considering the limited transaction processing capability of DLT, the authors suggest to adopt IPFS to handle the encrypted large data sets, then add the encrypted IPFS link to MAM for further exchangement. This research takes MAM as data transmission layer only that focuses on secure data exchanging architecture design and security analysis, but the trading strategies are not studied yet. A similar infrastructure proposed by Zichichi et al.\cite{SocialGood} is a smart transportation system. The authors offer a key and entry point management with MAM that minimize the information that data producers need to hold. Also, the trading procedure is automated and enforced with Ethereum smart contracts. However, the access control is examined by Authentication Service, the only client/server communication architecture, where the security issues and bottleneck of system emerges from, and the details of trading are not illustrated in this paper.

Researches below adopt MAM as data storage and transmit data with it as well. The industrial data marketplace\cite{IOTAIdustryMarketplace} proposed by IOTA Foundation, targets for IoT data streams trading. Data streams are stored via MAM and paid in IOTA. Nevertheless, the platform design is centralized, where new devices require manual approval to be visible in the marketplace. O. Lamtzidis and J. Gialelis \cite{IOTASensorNode} proposed a distributed sensor node (SN) system to exchange data and establish a data monetization economy paradigm. The Back-End server helps SNs to accelerate data uploads to MAM, manages keys and metadatas of data streams, and evaluates data price according to it's quality. Furthermore, the Back-End server operates an user friendly interface of the marketplace and tackles all trading procedures. The heavy loading of Back-End server encounters the system scalability problem, single point failure as well as malicious attacks which may damage the profits of all players. And the pricing strategy is rather simple, which do not take subscription based diagram into consideration. The decentralized data marketplace in \cite{DDMSmartCities} is fully decentralized which does not exist any intermediate server but data providers only, data providers attach and trade data streams via MAM, and specific tags are added in transaction as an index for different usages, such as payment check and product information search. However, once the data amount grows rapidly, this searching specific transactions by tags approach may fail due to the massive amount of transactions returned. Moreover, it is difficult to filter out the interested information and to prevent adversaries spamming transactions.

>>>>

A. Colman et al. \cite{TrustedMarketplaceWearable} discussed on trading the sensitive data among wearables. Several security issues are well discussed and solved with DLTs in the paper, the system consists of multiple components that has its different responsibilities, such as data anonymizer eliminates keen information for privacy protection, access controller handles the key management and contract manager manages Ethereum smart contracts. While the trading processes are splited into multiple servers, and the request/response communication model is applied, the scalability problem of the marketplace remains.

In the following researches, Masked Authenticated Messaging (MAM)\cite{MAM} is regarded as a secure data transmission layer and data storage built on top of DLT which provides access control, tamperproof and authentication functionalities by tailoring messages to a channel. Jinzhi Lu et al.\cite{luDecentralizedDM} builds the data exchange system with MAM and IPFS\cite{IPFS}, a content-based addressing distributed storage system. Considering the limited transaction processing capability of DLT, the authors suggest to adopt IPFS to handle the encrypted large data sets, then add the encrypted IPFS link to MAM for further exchangement. This research takes MAM as data transmission layer only that focuses on secure data exchanging architecture design and security analysis, but the trading strategies are not studied yet. A similar infrastructure proposed by Zichichi et al.\cite{SocialGood} offer a key and entry points management with MAM that minimize the information which data producers need to hold. Also, Ethereum smart contract is used to maintain an authorized user list and to enable trading. However, the access control is examined by Authentication Service, the only client/server communication architecture, where the security issues and bottleneck of system emerges from, and the details of trading and iteractions between providers and consumers are not illustrated in this paper.

Researches below adopt MAM as data storage and a secure data transmission layer. The industrial data marketplace\cite{IOTAIdustryMarketplace} proposed by IOTA Foundation targets for IoT data streams trading. Service requesters call for proposal of interested data and accept/reject proposals from service providers. After a proposal is accepted, the requesters can access data streams stored via MAM and pay providers in IOTA tokens. This proposal matching and trading procedure can be automated without any human guidance\cite{IOTAIdustryMarketplaceWithoutHuman}. Nevertheless, this trading model does not take into account the refund and unsubscribe mechanism, the service requesters still need to pay even if they want to unsubscribe or the data does not meet expectations.

O. Lamtzidis and J. Gialelis \cite{IOTASensorNode} proposed a distributed sensor node system to exchange data and establish a data monetization economy paradigm. The Back-End server helps sensor nodes to accelerate data uploads to MAM, manages keys and metadatas of data streams, and evaluates data price according to it's quality. Furthermore, the Back-End server operates an user friendly interface of the marketplace and tackles all trading procedures. The heavy loading of Back-End server encounters the system scalability problem, single point failure as well as malicious attacks which may damage the profits of all players. And the pricing strategy allows buyout, but does not take subscribe/unsubscribe based diagram into consideration. The decentralized data marketplace in \cite{DDMSmartCities} is fully decentralized which does not exist any intermediate server but data providers only, data providers attach and trade data streams via MAM. With MAM, the data streams subscription is enabled, yet the conditions and details like refund and unsubscription are not discussed in this paper.
